Efficient pedigree recording for fast population genetics simulation

### 2018-06-07 forwards_paper.tex
minor adjustments

We implement simplification by starting at the end of the simulation,
and moving back up through history,
recording in the new tree sequence only that information necessary to construct the tree sequence
of the specified individuals.
This process of tracing ancestry back through time in a pedigree
was the motivation for Hudson's coalescent simulation algorithm~\citep{hudson1983properties},
so it is unsurprising that simplification uses many of the same tools
as the implementation of Hudson's algorithm in \msprime{} \citep{kelleher2016efficient}.
The main difference is that events in a coalescent simulation are random, \revpoint{1}{2}
while here they are predetermined by history.
An implementation in pseudocode is provided in Appendix~\ref{ss:simplify_algorithm},
and a python implementation as supplementary information.

@@

\paragraph{A final note:}
in preparing this manuscript,
we debated a number of possible terms for the embellished pedigree,
i.e., the ``pedigree with ancestral recombination information''.
Etymological consensus \citep{liberman2014little} has
``pedigree'' derived from the french ``pied de grue'' for the foot of a crane
(whose branching pattern resembles the bifurcation of a single parent-offspring relationship).
An analogous term for the embellished pedigree might then be \emph{nedigree},
from ``nid de grue'',
as the nest of a crane is a large jumble of (forking) branches.
We thought it would be confusing to use this term throughout the manuscript,
but perhaps it will prove useful elsewhere.

>>>>

We implement simplification by starting at the end of the simulation,
and moving back up through history,
recording in the new tree sequence only that information necessary to construct the tree sequence
of the specified individuals.
This process of tracing ancestry back through time in a pedigree
was the motivation for Hudson's coalescent simulation algorithm~\citep{hudson1983properties},
so it is unsurprising that simplification uses many of the same tools
as the implementation of Hudson's algorithm in \msprime{} \citep{kelleher2016efficient}.
The main difference is that events in a coalescent simulation are random, \revpoint{1}{2}
while in our simplification algorithm they are predetermined by history.
An implementation in pseudocode is provided in Appendix~\ref{ss:simplify_algorithm},
and a python implementation as supplementary information.

@@

\paragraph{A final note:}
in preparing this manuscript,
we debated a number of possible terms for the embellished pedigree,
i.e., the ``pedigree with ancestral recombination information'',
the object through which each tree of a tree sequence is threaded.
Etymological consensus \citep{liberman2014little} has
``pedigree'' derived from the french ``pied de grue'' for the foot of a crane
(whose branching pattern resembles the bifurcation of a single parent-offspring relationship).
An analogous term for the embellished pedigree might then be \emph{nedigree},
from ``nid de grue'',
as the nest of a crane is a large jumble of (forking) branches.
We thought it would be confusing to use this term throughout the manuscript,
but perhaps it will prove useful elsewhere.
